---
title: "Company Attitude Inferential Analysis"
author: "Rachael Kawira"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Background story
A company ran a survey on the attitude of the employees on the certain company parameters.
```{r summary}
summary(attitude)
```
## Analysis
The parameters rated were overall rating, complaints, privileges, learning, raises, critical and advance. All the parameters were rated out of 100. First let's check the correlation between the parameters to determine whether there is multicolinearity. As you can see there is no multicolinearity between the parameters.

```{r corr}
cor(attitude)
```

Now lets see that on a plot

```{r matrix, echo=FALSE}
cor_matrix <- cor(attitude)
heatmap(cor_matrix, symm = TRUE, col = colorRampPalette(c("red", "white", "blue"))(100), scale = "none")
```

Now lets put the factors in a linear regression to see how each factor affects the overall rating.

```{r linear, echo=FALSE}
linear_model <- lm(rating ~ complaints + privileges + learning + raises + critical + advance, data= attitude)
summary(linear_model)
```
Complaints has the biggest weight on the overall rating. The learning, raises and critical parameters have a positive correlation to the overall rating while privileges and advances are inversely correlated to the overall rating.
